Spin canonical divisors of log stacky curves

### 2015-06-24 stacky_write_up/spin_cring.tex
shift/reword g=0 and g=1 theorems

These are our results.
\begin{thm}
\label{thm:g_0_generators_relations}
Let $(\sx, \Delta, \halfcan)$ log spin curve over a perfect field $k$, so
that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; \delta)$. Then the
canonical ring

@@

\noindent
is generated as a $k$-algebra by elements of degree at most $e = 
\max(5,e_1,\ldots, e_r).$ If the genus $g \geq 2,$ then $R(\sx, \Delta, \halfcan)$ has relations in degree at most $\max(11,e_1,\ldots, e_r).$ If the genus $g = 0$ or $g = 1,$ then $R(\sx, \Delta, \halfcan)$ has relations in degree at most $\max(10,e_1,\ldots, e_r),$ so
long as $\sigma$ does not lie in a finite list of exceptional cases, as listed in Table ~\ref{table:g-1-exceptional} for signatures with $g = 1$ and Table ~\ref{table:g-0-exceptional} for signatures with $g = 0$.
\end{thm}

@@

@@

\todo{Aaron: Use thmrestate instead of rewriting the Theorem}
\begin{thm}
\label{thm:g_0_generators_relations_rep}
Let $(\sx, \Delta, L)$ be a tame log spin curve over a perfect field $k$, so
that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; \delta)$. Then the
canonical ring

\begin{align*}
	R(\sx, \Delta, L) = \bigoplus_{d = 0}^\infty H^0(\sx, \sco(L)^{\otimes d})
\end{align*}

\noindent
is generated as a $k$-algebra by elements of degree at most $e = 
\max(5,e_1,\ldots, e_r)$ with relations in degree at most $2e$, so 
long as $\sigma$ does not lie in a finite list of exceptions. \todo{
Include reference to the table with this list of exceptions.}
\end{thm}

>>>>

These are our results.
\begin{thm}
\label{thm:general_generators_relations}
Let $(\sx, \Delta, \halfcan)$ log spin curve over a perfect field $k$, so
that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; \delta)$. Then the
canonical ring

@@

\noindent
is generated as a $k$-algebra by elements of degree at most $e =
\max(5, e_1, \ldots, e_r).$ If the genus $g \geq 2,$ then $R(\sx,
\Delta, \halfcan)$ has relations in degree at most $\max(11, e_1,
\ldots, e_r).$ If the genus $g = 0$ or $g = 1,$ then $R(\sx, \Delta
, \halfcan)$ has relations in degree at most $\max(10, e_1, \ldots,
e_r),$ so long as $\sigma$ does not lie in a finite list of
exceptional cases, as listed in Table ~\ref{table:g-1-exceptional}
for signatures with $g = 1$ and Table ~\ref{table:g-0-exceptional}
for signatures with $g = 0$.
\end{thm}

@@

\begin{thm}
\label{thm:g_1_generators_relations}
Let $(\sx, \Delta, \halfcan)$ log spin curve over a perfect field $k$,
so that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; \delta)$.
If $g = 1$, then the canonical ring

\noindent
is generated as a $k$-algebra by elements of degree at most $e =
\max(5, e_1, \ldots, e_r)$ and has relations in degree at most $\max
(10, e_1, \ldots, e_r),$ so long as $\sigma$ does not lie in a
finite list of exceptional cases, as listed in Table
~\ref{table:g-1-exceptional}.
\end{thm}

@@

\begin{thm}
\label{thm:g_0_generators_relations}
Let $(\sx, \Delta, \halfcan)$ log spin curve over a perfect field $k$,
so that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; \delta)$.
If $g = 0$, then the canonical ring

\noindent
is generated as a $k$-algebra by elements of degree at most $e =
\max(5, e_1, \ldots, e_r)$ and has relations in degree at most $\max
(10, e_1, \ldots, e_r),$ so long as $\sigma$ does not lie in a
finite list of exceptional cases, as listed in Table
~\ref{table:g-0-exceptional}.
\end{thm}
